Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/results.tex
formatting revisions

\begin{table}
\centering
\begin{tabular}{ccc}
\toprule
                   & \multicolumn{2}{c}{Starting Configuration} \\
\hline
Monomers per layer & Sandwiched & Parallel Displaced \\
\midrule
4 & $3.71 \pm 0.08$ & $3.82 \pm 0.06$ \\
5 & $3.99 \pm 0.08$ & $4.16 \pm 0.09$ \\
6 & $4.83 \pm 0.08$ & $4.85 \pm 0.05$ \\
7 & $4.73 \pm 0.06$ & $4.84 \pm 0.06$ \\
8 & $5.08 \pm 0.08$ & $5.46 \pm 0.07$ \\
\bottomrule
\end{tabular}
\caption{The pore spacing of the model increases as number of monomers
in each layer increases. The pore spacing of a system starting in the 
sandwiched configuration is systematically lower than that started in an 
offset configuration. Systems built with 5 monomers per layer in a parallel
displaced configuration results in a pore spacing closest to experimental
data}\label{table:p2p} 
\end{table}

\begin{figure}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
	\caption{Pair distribution functions of aromatic carbons for the
	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
	parallel displaced configurations. Spikes in the distribution mark
	distinct layers. The magnitude of the spikes with respect to the 
	average suggest that the 5 monomer per layer, sandwiched configuration
	possesses the highest degree of layer partitioning.}\label{fig:zdf}
\end{figure}

@@

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:280K_pore}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close.png}
                \caption{}\label{fig:340K_pore}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{p2p_tramp.png}
                \caption{}\label{fig:p2p_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{thickness_tramp.png}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{rzlayeredrestrained.png}
		\caption{}\label{fig:rzplayeredrestrained}
	\end{subfigure}
	\begin{subfigure}{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{rzoffsetrestrained.png}
		\caption{}\label{fig:rzoffsetrestrained}
	\end{subfigure}
	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
	with restraints placed on aromatic carbons shows all major features
	present experimental WAXS. Near solid lines at constant z are a result of 
	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
	restrained parallel displaced configuration may also contained all
	major experimental WAXS features. One can argue that R-spots is not present
	but it is difficult to distinguish because of its intersection with the solid
	R-helix line. Longer simulations are necessary to determine which structure
	is the best match to experiment}\label{fig:XRDrestrained}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{(a) All major features except R-helix are present in
	XRD patterns resulting from an equilibrated sandwiched configuration 
	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
	(b) All major features execpt R-spots are present in XRD patterns 
	resulting from an equilibrated parallel displaced configuration in Basin A.
	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
	are the only major features present in XRD patterns resulting from an 
	equilibrated disordered phase}\label{fig:XRDsim}
\end{figure}

The spots that appear in the simulated XRD pattern of the sandwiched
conformation are a result of the way alkane tails pack together. Previously,
the spots in the diffraction pattern had been explained as the product of
tilted alkane chains. We measured the tilt angle of the alkane chains and 
showed that our system equilibrates to an average tilt angle close to zero 
degrees (Figure~\ref{fig:tilt}). To understand the origin of the spots, we 
determined which atoms gave rise to the feature. By removing atoms from 
the trajectory and simulating a diffraction pattern, we were able to isolate
the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}. Since the tails are mostly flat, we
plotted the centroids of the tails and measured the angle between each centroid 
and its nearest neighbors with respect to the plane of the membrane (Figure~\ref{centroids}). The 
distribution of these angles is consistent with the location of the spots (Figure~\ref{fig:angle_distribution}).
We reason that monomer tails stacked closely in the sandwiched conformation
are forced to splay apart and pack in between in each other which creates a
nearly hexagonal array of packed tails.

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{tails_topview.png}
		\caption{}\label{fig:tails_topview}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{centroids_box.png}
		\caption{}\label{fig:centroids}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{angles_traj_layered.png}
		\caption{}\label{fig:angle_distribution}
	\end{subfigure}
	\caption{(a) The trajectory can be stripped of all atoms except carbon
	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
	distribution created by measuring the angle between each centroid (e.g. red 
	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
	plane has distinct spikes near 30\degree, which is consistent with the location
	of R-spots}\label{fig:tail_packing}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
\end{figure}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
                   & \multicolumn{2}{c}{Starting Configuration} \\
\hline
Monomers per layer & Sandwiched & Parallel Displaced \\
\midrule
4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
5 & $3.99 \pm 0.04$ & $4.16 \pm 0.04$ \\
6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
\bottomrule
\end{tabular}
\caption{The pore spacing of the model increases as number of monomers
in each layer increases. The pore spacing of a system starting in the 
sandwiched configuration is systematically lower than that started in an 
offset configuration. Systems built with 5 monomers per layer in a parallel
displaced configuration results in a pore spacing closest to experimental
data}\label{table:p2p} 
\end{table}

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
	\caption{Pair distribution functions of aromatic carbons for the
	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
	parallel displaced configurations. Spikes in the distribution mark
	distinct layers. The magnitude of the spikes with respect to the 
	average suggest that the 5 monomer per layer, sandwiched configuration
	possesses the highest degree of layer partitioning.}\label{fig:zdf}
\end{figure}

@@

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{280K_tramp_close.png}
                \caption{}\label{fig:280K_pore}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{340K_tramp_close.png}
                \caption{}\label{fig:340K_pore}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{p2p_tramp.png}
                \caption{}\label{fig:p2p_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{thickness_tramp.png}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.475\textwidth}
		\hspace{-1.2cm}
		\centering
		\includegraphics[width=\textwidth,valign=t]{rzlayeredrestrained.png}
		\caption{}\label{fig:rzplayeredrestrained}
	\end{subfigure}
	\begin{subfigure}{0.475\textwidth}
		\hspace{-1.2cm}
		\centering
		\includegraphics[width=\textwidth,valign=t]{rzoffsetrestrained.png}
		\caption{}\label{fig:rzoffsetrestrained}
	\end{subfigure}
	\caption{(a) Simulated X-ray diffraction of a sandwiched configuration
	with restraints placed on aromatic carbons shows all major features
	present in experimental WAXS. Near solid lines at constant z are a result of 
	the highly ordered aromatic rings. (b) Simulated X-ray diffraction of a similarly
	restrained parallel displaced configuration may also contain all
	major experimental WAXS features. One can argue that R-spots is not present
	but it is difficult to distinguish because of its intersection with the solid
	R-helix line. Longer simulations are necessary to determine which structure
	is the best match to experiment}\label{fig:XRDrestrained}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\hspace{-0.9cm}
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{(a) All major features except R-helix are present in
	XRD patterns resulting from an equilibrated sandwiched configuration 
	in Basin A. R-pi intersescts R-alkanes. R-helix faded during equilbration.
	(b) All major features execpt R-spots are present in XRD patterns 
	resulting from an equilibrated parallel displaced configuration in Basin A.
	R-helix exists faintly in the expected location. (c) R-pores and R-alkanes
	are the only major features present in XRD patterns resulting from an 
	equilibrated disordered phase}\label{fig:XRDsim}
\end{figure}

@@

The spots that appear in the simulated XRD pattern of the sandwiched
conformation are a result of the way alkane tails pack together. Previously,
the spots in the diffraction pattern had been explained as the product of
tilted alkane chains. We measured the tilt angle of the alkane chains and 
showed that our system equilibrates to an average tilt angle close to zero 
degrees (Figure~\ref{fig:tilt}). To understand the origin of the spots, we 
determined which atoms gave rise to the feature. By removing atoms from 
the trajectory and simulating a diffraction pattern, we were able to isolate
the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}). Since the tails are mostly flat, we
plotted the centroids of the tails and measured the angle between each centroid 
and its nearest neighbors with respect to the plane of the membrane (Figure~\ref{fig:centroids}). The 
distribution of these angles is consistent with the location of the spots (Figure~\ref{fig:angle_distribution}).
We reason that monomer tails stacked closely in the sandwiched conformation
are forced to splay apart and pack in between in each other which creates a
nearly hexagonal array of packed tails.

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\hspace{-1cm}
		\vspace{1cm}
		\includegraphics[width=\textwidth,scale=2]{tails_topview.png}
		\caption{}\label{fig:tails_topview}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{centroids_box.png}
		\caption{}\label{fig:centroids}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{angles_traj_layered.png}
		\caption{}\label{fig:angle_distribution}
	\end{subfigure}
	\caption{(a) The trajectory can be stripped of all atoms except carbon
	atoms in monomer tails. (b) Simulated diffraction of the tail-only trajectory
	still gives rise to R-spots. (c) Finding the center of mass and visualizing 
	their coordinates reveals the hexagonal-like packing of the tails. (d) The 
	distribution created by measuring the angle between each centroid (e.g. red 
	in (c)) and its neareset neighbors (e.g. green in (c)) with respect to the xy
	plane has distinct spikes near 30\degree, which is consistent with the location
	of R-spots}\label{fig:tail_packing}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_diagram.PNG}
		\caption{}\label{fig:p2p_diagram}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{no_xlink_p2p.png}
		\caption{}\label{fig:no_xlink_p2p}
	\end{subfigure}
		\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{xlink_p2p.png}
		\caption{}\label{fig:xlink_p2p}
	\end{subfigure}
	\caption{(a) The legends of the plots in (b) and (c) refer to the numbers shown.
	Each numbered circle represents a pore. Distances are measured along each of the 
	lines shown in addition to the distance from pore 1 to pore 4. (b) The positions
	of individual pores fluctuate in an uncrosslinked system. (c) The positions of
	individual pores in the crosslinked system are stable relative to the uncrosslinked
	system}\label{fig:xlink}
\end{figure}
